 

### 2023-05-11 paper3.Rmd
Adding section on population weighting in Paper 3.
Final revisions to manuscript

paper3_abstract <- paste0("For searches related to depression, I observed a sustained decline in search density of ",
             function_dynamic_text_results("main","depression", "slope" , TRUE, TRUE), " and an immediate downward level shift of ",
             function_dynamic_text_results("main","depression", "intercept", TRUE),
             " relative to comparable symptom searches. For anxiety, I estimated a similar slope change of ",
             function_dynamic_text_results("main","anxiety", "slope", TRUE), 
             " and a level shift of ",
             function_dynamic_text_results("main","anxiety", "intercept", TRUE),
 ". I did not observe significant variations across predominately Democrat or Republican voting states and counties, and the findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")

@@

{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the United States (US) is a lack of appropriate high frequency surveillance data. A potential marker of population mental health is the use of Internet search data, which enables real-time, large-scale analysis of evolving mental health issues.

{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in US states and counties. I examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptoms compared with physical health symptoms, and estimated associations between vaccine announcement and changes in mental health symptom search density. I adjusted for state, month, and weekday effects, and applied numerous sensitivity analyses to assess the robustness of the findings. To explore heterogeneity by predominate political affiliation, I also tested whether the estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.

{\bf Findings and interpretation:} Under the main model specification, I observed reduced search density for depression and anxiety associated with the announcement of vaccine safety data. `r paper3_abstract` If symptom search density echoes population health, the results would indicate that announcements regarding the development of safe and effective COVID-19 vaccines led to a robust and sustained improvement in mental health. These findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.

@@

While COVID-19 continues to bring unprecedented challenges to societies around the world, the development and distribution of safe and effective vaccines has fundamentally changed the trajectory of the pandemic. Beyond the physical benefits vaccines provide in reducing the risk of infection and associated morbidity and mortality, a growing body of evidence suggests that vaccination has also
contributed to improved mental health.[@agrawalImpactCOVID19Vaccine2021; @chourpiliadisShorttermImprovementMental2023; @nguyenPsychologicalBenefitsCOVID192021; @rubinsteinEffectCOVID19Vaccinations2023] While there is limited international data on the secondary mental health impact of COVID-19 vaccination, research drawing from the \acr{US} Census Bureau’s Household Pulse Survey has found that benefits of vaccination may include up to a 30% reduction in symptoms of anxiety and depression among vaccinated adults,[@agrawalImpactCOVID19Vaccine2021] while research using the University of Southern California Understanding America Survey suggests a reduction in loneliness associated with greater social interactions following vaccination.[@leeEffectVaccinationSocial2022]

@@

A key obstacle to studying the impact of public health policies on population mental health, however, is a lack of appropriate high frequency surveillance data. A potential marker of population mental health is the use of internet search data, which enables real-time, large-scale analysis of evolving mental health issues. A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020] found a strong correlation between search trends for depression and anxiety with indicators of mental health services utilization (reported in the \acr{US} Census Household Pulse Survey) and rates of emergency department visits for mental health conditions (from the National Syndromic Surveillance Program of the \acr{US} \acr{CDC}).[@vaidyanathanEvaluationInternetSearches2022] If taken as a reasonable proxy for mental health disorders, search data can provide valuable information on how population mental health reacts to real-time events, enabling policymakers to better respond to mental health needs in a timely manner.

@@

Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominately English-speaking countries: Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States. In the \acr{US}, subnational regions include states and counties. Because the aggregated search density data were constructed based on relative search population within each region, I could not compare search density for specific symptoms across different regions; however, comparing search density within regions (or a group of regions) was feasible both over time and across different symptoms.

@@

Population estimates for 2020 by \acr{FIPS} code were obtained from the\acr{USDA} Economic Research Service.

@@

```
I applied this model for all available `r diseases_n` diseases with county-level data. As search density may rapidly change in response to new announcements, I trimmed the bandwidth of dates to fit the model to 40 days before and after November 16, 2020.

@@

Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (\acr{CIs}) using heteroskedasticity-robust standard errors.

@@

Slope changes and level shifts for anxiety, depression, and \acr{MDD} are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}. Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates compared to state level estimates, but with much tighter \acr{CIs}, even when geographic fixed effects and narrower bandwidths were included. Across all models, the sustained change in search density for anxiety and depression was negative and significant with an alpha of 0.01. In terms of the estimated level shifts, `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models for anxiety (`r round(function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)*100/144,0)`%) had a statistically significant negative change, compared to `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "positive", multiverse_p = 0.01)` models with a positive one. For depression, of the `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "positive", multiverse_p = 0.01) + function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models with a statistically significant level shift estimate, all `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models returned a negative level shift coefficient.

@@

Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and \acr{MDD} as found in the main analysis (Figure \ref{fig_political}). This was particularly observed in the analysis of \acr{US} state-level data, where confidence intervals for the \acr{CITS} effect estimates were statistically equivalent across red and blue states. In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties than blue ones, with minor overlap in confidence intervals. The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties. Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` versus `r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.

@@

These findings should be interpreted with some limitations in mind. First, the aggregated and anonymized nature of the data imposes a constraint to the interpretations, as it was not possible to identify whether individual political ideologies were correlated with changes in search trends. Instead, I relied on population aggregates that reflect political orientation (i.e., vote share by county and state) as a proxy, focusing on the 20% most Democrat and Republican-voting areas to strengthen the plausibility of this proxy. In addition, the use of Google search density as a proxy for population mental health could not be directly validated in the study, as the search data was anonymized and aggregated. While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and \acr{US} population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.

Despite these limitations, the findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms. If symptom search density echoes population health, the results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination. These findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.

>>>>

paper3_abstract <- paste0("For searches related to depression, I observed a sustained decline in search density of ",
             function_dynamic_text_results("main","depression", "slope" , TRUE, TRUE), " and an immediate downward level shift of ",
             function_dynamic_text_results("main","depression", "intercept", TRUE),
             " relative to comparable symptom searches. For anxiety, I estimated a similar slope change of ",
             function_dynamic_text_results("main","anxiety", "slope", TRUE), 
             " and a level shift of ",
             function_dynamic_text_results("main","anxiety", "intercept", TRUE),
 ". I did not observe significant variations across predominantly Democrat or Republican voting states and counties, and the findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")

@@

{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the United States (US) is a lack of appropriate high-frequency surveillance data. A potential marker of population mental health is the use of Internet search data, which enables real-time, large-scale analysis of evolving mental health conditions

{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to depression and anxiety in US states and counties. I examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptom searches compared with physical health symptom searches, and estimated associations between vaccine announcement and changes in mental health symptom search density. I adjusted for state, month, and weekday effects, and applied numerous sensitivity analyses to assess the robustness of the findings. To explore heterogeneity by predominant political affiliation, I also tested whether the estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.

{\bf Findings and interpretation:} Under the main model specification, I observed reduced search density for depression and anxiety associated with the announcement of vaccine safety data. `r paper3_abstract` If symptom search density echoes population health, the results would indicate that announcements regarding the development of safe and effective COVID-19 vaccines led to a robust and sustained improvement in mental health. These findings underscore the importance of timely and transparent communication and highlight the potential application of high-frequency internet search data for population mental health surveillance.

@@

While COVID-19 continues to bring unprecedented challenges to societies around the world, the development of safe and effective vaccines has fundamentally changed the trajectory of the pandemic. Beyond the physical benefits vaccines provide in reducing the risk of infection and associated morbidity and mortality, a growing body of evidence suggests that vaccination has also
contributed to improved mental health.[@agrawalImpactCOVID19Vaccine2021; @chourpiliadisShorttermImprovementMental2023; @nguyenPsychologicalBenefitsCOVID192021; @rubinsteinEffectCOVID19Vaccinations2023] While there is limited international data on the secondary mental health impact of COVID-19 vaccination, research drawing from the \acr{US} Census Bureau’s Household Pulse Survey has found that benefits of vaccination may include up to a 30% reduction in symptoms of anxiety and depression among vaccinated adults,[@agrawalImpactCOVID19Vaccine2021] while research using the University of Southern California Understanding America Survey suggests a reduction in loneliness associated with greater social interactions following vaccination.[@leeEffectVaccinationSocial2022]

@@

A key obstacle to studying the impact of public health policies on population mental health, however, is a lack of appropriate high-frequency surveillance data. A potential marker of population mental health is the use of internet search data, which enables real-time, large-scale analysis of evolving mental health issues. A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020] found a strong correlation between search trends for depression and anxiety with indicators of mental health services utilization (reported in the \acr{US} Census Household Pulse Survey) and rates of emergency department visits for mental health conditions (from the National Syndromic Surveillance Program of the \acr{US} \acr{CDC}).[@vaidyanathanEvaluationInternetSearches2022] If taken as a reasonable proxy for mental health disorders, search data can provide valuable information on how population mental health reacts to real-time events, enabling policymakers to better respond to mental health needs in a timely manner.

@@

Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominantly English-speaking countries: Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States. In the \acr{US}, subnational regions include states and counties. Because the aggregated search density data were constructed based on relative search population within each region, I could not compare search density for specific symptoms across different regions; however, comparing search density within regions (or a group of regions) was feasible both over time and across different symptoms.

@@

Population estimates for 2020 by \acr{FIPS} code were obtained from the \acr{USDA} Economic Research Service.

@@

```
I applied this model for all available `r diseases_n` diseases with county-level data, weighted by population size. As search density may rapidly change in response to new announcements, I trimmed the bandwidth of dates to fit the model to 40 days before and after November 16, 2020.

@@

Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals ( \acr{CIs}) using heteroskedasticity-robust standard errors.

@@

Slope changes and level shifts for anxiety, depression, and \acr{MDD} are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}. Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates compared to state level estimates, but with much tighter \acr{CIs}, even when geographic fixed effects and narrower bandwidths were included. Across all models, the sustained changes in search density for anxiety and depression were negative and significant with an alpha of 0.01. In terms of the estimated level shifts, `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models for anxiety (`r round(function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)*100/144,0)`%) had a statistically significant negative change, compared to `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "positive", multiverse_p = 0.01)` models with a positive one. For depression, of the `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "positive", multiverse_p = 0.01) + function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models with a statistically significant level shift estimate, all `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models returned a negative level shift coefficient.

@@

Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and \acr{MDD} as found in the main analysis (Figure \ref{fig_political}). This was particularly observed in the analysis of \acr{US} state-level data, where confidence intervals for the \acr{CITS} effect estimates were statistically equivalent across red and blue states. In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties compared to blue ones, with minor overlap in confidence intervals. The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties. Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` versus `r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.

@@

These findings should be interpreted with some limitations in mind. First, the aggregated and anonymized nature of the data imposes a constraint to the interpretations, as it was not possible to identify whether individual political ideologies were correlated with changes in search trends. Instead, I relied on population aggregates that reflect political orientation (i.e., vote share by county and state) as a proxy, focusing on the 20% most Democrat and Republican-voting areas to strengthen the plausibility of this proxy. In addition, the use of Google search density as a proxy for population mental health could not be directly validated in the study, as the search data was anonymized and aggregated. While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and \acr{US} population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high-frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.

Despite these limitations, the findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms. If symptom search density echoes population health, the results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination. These findings underscore the importance of timely and transparent communication and highlight the potential application of high-frequency internet search data for population mental health surveillance.

### 2023-05-11 thesis_final_version.Rmd
Final revisions to manuscript

bibliography: main.bib
# natbiboptions: "numbers"
csl: https://www.zotero.org/styles/the-lancet

  # intro: intro.bib
  # ch1: chapter1.bib
  #

acronyms:
  insert_loa: false
  loa_title: ""

  # loa_title: "List of Acronyms"
  keys:
    - shortname: LMIC
      longname: low and middle income country

---

@@

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. To capture premature mortality due to mental disorders, as well as disability from associated causes, we proposed a composite approach to estimation. Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. The economic value of this mental health burden was estimated to exceed 4.7 trillion USD using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.

In Chapter 2, we focused on Madagascar—a low income country that is among the most vulnerable to the health consequences of climate change—and examine how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones. Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.  Our results indicated that warmer temperatures in the cooler central highlands were associated with a decrease in monthly reported visits for mental disorders, while higher soil moisture could lead to an increase in visits, particular in high flood-risk regions and after a three-month lag, indicating potential variation in the impact of climate change on mental health needs and system responses.

In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from U.S. counties, states, and international trends, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

@@

```{r todo}

### TO DO / KNOWN ISSUES

# Acronyms with acronym down
# Separate bibliography for each section
# Numbered figures and tables by section

# Check that sequential articles are represented by a dash
# Table of figures and tables
# Institutional authors need to be fixed in bibliography

```

>>>>

bibliography: main.bib
csl: https://www.zotero.org/styles/the-lancet
acronyms:
  insert_loa: false
  insert_links: false
  loa_title: ''
  keys:
    - shortname: DALYs
      longname: disability-adjusted life years
    - shortname: YLLs
      longname: years of life lost 
    - shortname: YLDs
      longname: years of healthy life lost due to disability 
    - shortname: LMICs
      longname: low- and middle-income countries
    - shortname: WHO
      longname: World Health Organization
    - shortname: USD
      longname: United States dollars
    - shortname: GBD
      longname: Global Burden of Disease
    - shortname: GBO
      longname: Global Health Observatory
    - shortname: GDP
      longname: gross domestic product
    - shortname: NCDs
      longname: noncommunicable diseases
    - shortname: PAF
      longname: population attributable fraction
    - shortname: VSL
      longname: value of a statistical life
    - shortname: IRB
      longname: Institutional Review Board 
    - shortname: UIs
      longname: uncertainty intervals
    - shortname: CIs
      longname: confidence intervals
    - shortname: PPP
      longname: purchasing power parity
    - shortname: CCEs
      longname: climate change-related exposures
    - shortname: HMIS
      longname: health management information system
    - shortname: ESA CCI
      longname: European Space Agency’s Climate Change Initiative
    - shortname: ESA CCI SM
      longname: ESA CCI soil moisture dataset
    - shortname: ERA5
      longname: 'European ReAnalysis 5' 
    - shortname: NOAA
      longname: United States National Oceanic and Atmospheric Administration
    - shortname: GESIS
      longname: Gestion du Système d'Information Sanitaire
    - shortname: DHIS2
      longname: 'District Health Information Software 2'
    - shortname: CSB
      longname: centre santé de base
    - shortname: FSB
      longname: formation sanitaires privées de dase
    - shortname: CHD/CHRD
      longname: centre hospitalier de référence de district
    - shortname: RHINO
      longname: Routine Health Information Network
    - shortname: USAID
      longname: United States Agency for International Development
    - shortname: US
      longname: United States
    - shortname: CHRR
      longname: centre hospitalier de référence régionale
    - shortname: CHU
      longname: centre hospitalier universitaire
    - shortname: C3S
      longname: Copernicus Climate Change Service
    - shortname: ECMWF
      longname: European Centre for Medium-Range Weather Forecasts
    - shortname: km
      longname: kilometers
    - shortname: MFR La Réunion
      longname: Météo-France La Réunion
    - shortname: WMO
      longname: World Meteorological Organization
    - shortname: RSMC 
      longname: Regional Specialized Meteorological Center
    - shortname: NB
      longname: negative binomial
    - shortname: IRRs
      longname: incidence rate ratios
    - shortname: FE
      longname: fixed effects
    - shortname: CDC
      longname: Centers for Disease Control and Prevention
    - shortname: FDA
      longname: Food and Drug Administration
    - shortname: EUA
      longname: Emergency Use Authorization
    - shortname: MIT
      longname: Massachusetts Institute of Technology
    - shortname: FIPS
      longname: Federal Information Processing Standards
    - shortname: USDA
      longname: United States Department of Agriculture
    - shortname: ITS
      longname: interrupted time series
    - shortname: CITS
      longname: controlled interrupted time series
    - shortname: MDD
      longname: major depressive disorder
    - shortname: ADHD
      longname: attention deficit hyperactivity disorder
    - shortname: CoC
      longname: clouding of consciousness
    - shortname: GAD
      longname: generalized anxiety disorder
---

@@

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. To capture premature mortality due to mental disorders, as well as disability from associated causes, we proposed a composite approach to estimation. Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. The economic value of this mental health burden was estimated to exceed 4.7 trillion United States dollars using a value of a statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.

In Chapter 2, we focused on Madagascar—a low-income country that is among the most vulnerable to the health consequences of climate change—and examined how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones. Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020, we conducted an ecological analysis using negative binomial regression. Our results indicated that warmer temperatures in the cooler central highlands were associated with a decrease in monthly reported visits for mental disorders, while higher soil moisture could lead to an increase in visits, particular in high flood-risk regions and after a three-month lag, indicating potential variation in the impact of climate change on mental health needs and system responses.

In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent public health communication and illustrate the potential application of high-frequency internet search data for population mental health surveillance.

@@

<!-- ```{r todo} -->

<!-- ### TO DO / KNOWN ISSUES -->

<!-- # Check that sequential articles are represented by a dash -->
<!-- # Institutional authors need to be fixed in bibliography -->
<!-- # Numbered figures and tables by section -->

<!-- ``` -->
